TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-20 paper/draft.tex
selection fig descriptions

The three panels of \ref{fig:safe_selection} show before and after selection of the sources in \gaia\ color-magnitude space, colored by \thecannon\ determined temperatures, metallicities, and spectral types, with their respective training samples overplotted in orange. Comparisons between the West-trained spectral types and Mann-trained temperatures and metallicities are shown in Figure \ref{fig:west_vs_mann}: left shows the slight negative correlation between spectral type and [Fe/H], and right shows the nonlinear decrease in temperature with visible metallicity gradient. We also note that applying our model requires very little computational demand: the time to train and test a model on all 14,827 sources was two minutes on a personal laptop.

% JB: NOW POINT TO RESULTS FIGURES AND SUMMARIZE THEM, IF THERE IS ANYTHING ELSE?

@@

\begin{figure}[ht]
% \gridline{\fig{figures/safe_selection_teff.png}{0.5\textwidth}{}
%           \fig{figures/safe_selection_feh.png}{0.5\textwidth}{}}
% \gridline{\fig{figures/safe_selection_spt.png}{0.5\textwidth}{}}
\plottwo{figures/cmd_teff_full.png}{figures/cmd_teff_safe.png}
\plottwo{figures/cmd_feh_full.png}{figures/cmd_feh_safe.png}
\plottwo{figures/cmd_spt_full.png}{figures/cmd_spt_safe.png}
\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 10,311 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, binaries, and K dwarfs). Overplotted with orange triangles are the M15 and W11 training samples, for their respective \cannon\ test labels. Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases with increasing absolute magnitude as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence. \label{fig:safe_selection}}
\end{figure}

>>>>

The three panels of \ref{fig:safe_selection} show before and after selection of the sources in \gaia\ color-magnitude space, colored by \thecannon\ determined temperatures, metallicities, and spectral types, with their respective training samples overplotted in orange. Each plot shows the expected gradient: temperature increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly to the main sequence branch. Additionally we notice a slight deviation at the upper slice of the main sequence where \cannon\ temperatures, metallicities and spectral types all appear lower than the gradient trends in the rest of the branch, which is most likely the binary sequence. Comparisons between the West-trained spectral types and Mann-trained temperatures and metallicities are shown in Figure \ref{fig:west_vs_mann}: left shows the slight negative correlation between spectral type and [Fe/H], and right shows the nonlinear decrease in temperature with visible metallicity gradient. We also note that applying our model requires very little computational demand: the time to train and test a model on all 14,827 sources was two minutes on a personal laptop.

@@

\begin{figure}[ht]
% \gridline{\fig{figures/safe_selection_teff.png}{0.5\textwidth}{}
%           \fig{figures/safe_selection_feh.png}{0.5\textwidth}{}}
% \gridline{\fig{figures/safe_selection_spt.png}{0.5\textwidth}{}}
\plottwo{figures/cmd_teff_full.png}{figures/cmd_teff_safe.png}
\plottwo{figures/cmd_feh_full.png}{figures/cmd_feh_safe.png}
\plottwo{figures/cmd_spt_full.png}{figures/cmd_spt_safe.png}
\caption{Full sample of 14,827 M dwarfs colored by \cannon\ labels before selection (left) and final sample selection of 10,311 M dwarfs after applying selection criteria described in Section \ref{subsec:test_selection} (right), to reduce contamination from sources with that are not similar to the training sample (not single, main-sequence M stars, such as pre-main sequence, binaries, and K dwarfs). Overplotted with orange triangles are the M15 and W11 training samples, for their respective \cannon\ test labels. Temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases perpendicularly up from the main sequence branch as expected. Deviations from these gradients seen at the upper slice of the main sequence is likely remaining contamination from the binary sequence. \label{fig:safe_selection}}
\end{figure}
